Red-Giant Hot Jupiters: Brilliant Radio Emitter?

### 2015-05-16 ms.tex
figure is updated
description added

They are compared with numerical simulations in \citep{christensen2010}. We employ the following relationship \citep{christensen2006}, which was found to be in a good agreement with the numerical experiments over a wide parameter space \memoYF{describe in more detail}:
%%%%%%%%%% 
\begin{equation}
B^2 \propto \rho_c r_c^{4/3} q_c^{2/3},% \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
\end{equation}
%%%%%%%%%%
where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region.

In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of planets. 
In this paper, we consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, as the numerical calculations show that the radii of gaseous planets over the range of $0.1 R_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ in 1 Gyr \citep{fortney2007}. 
For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
%%%%%%%%%% 
\begin{equation}
\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
\end{equation}
%%%%%%%%%%
We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_c=700\,\mbox{kg/m}^3$ \memoYF{cite something!}. The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core. 
In the case of Jupiter, $r_{c,\,J} = 0.85 R_{\rm J}$. 
%We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Estimate of Planetary Magnetic Field}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[bp]
   \plotonesc{contour_B.pdf}
   \caption{Planetary magnetic field as a function of age and planetary mass, based on \citet{christensen2010}. }
  \label{fig:radio}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Estimate of Radio emission of RGHJs in comparison with canonical HJs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

They are compared with numerical simulations in \citep{christensen2010}. We employ the following relationship \citep{christensen2006}, which was found to be in a good agreement with the numerical experiments over a wide parameter space \memoYF{describe in more detail}:
%%%%%%%%%% 
\begin{equation}
B^2 \propto \rho_c r_c^{4/3} q_c^{2/3}, \label{eq:Bscaling} % \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta } 
\end{equation}
%%%%%%%%%%
where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region.

In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of planets. 
In this paper, we consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, as the numerical calculations show that the radii of gaseous planets over the range of $0.1 R_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ in 1 Gyr \citep{fortney2007}. 
For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
%%%%%%%%%% 
\begin{equation}
\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
\end{equation}
%%%%%%%%%%
We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=700\,\mbox{kg/m}^3$ \memoYF{cite something!}. The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core. 
In the case of Jupiter, $r_{c,\,J} = 0.85 R_{\rm J}$. 
%We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Estimate of Planetary Magnetic Field and Maximum Frequency}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%s

First, we estimate the strength of planetary magnetic field based on the scaling relation of equation (\ref{eq:Bscaling}) and assumptions described in \S\ref{ss:magneticfield}. 
Figure \ref{fig:planetaryB} shows the estimated core radius ($r_c$), core density ($\rho_c$), and convected heat flux ($q_c$) as well as the predicted magnetic field strength at planetary surface ($B$) and the corresponding cyclotron frequency ($f_c$), as functions of planetary mass and the age. 
Planetary magnetic field is expected to become stronger as planet becomes larger because all of $r_c$, $\rho _c$, and $q_c$ in equation (\ref{eq:Bscaling}) increase with planetary mass.

The cyclotron frequency Jovian planets older than 10~Gyr typically larger than 10~MHz, the plasma cut-off frequency of Earth's ionosphere, and less than 1~GHz. 
In this regime, there are a number of current and near-future radio wave detectors including UTR-2, LOFAR, LWA, and SKA.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
%   \plotoneh{r_c.pdf}
%   \plotoneh{rho_c.pdf}
   \plotoneh{model_planetaryB.pdf}
   \caption{Planetary magnetic field as a function of age and planetary mass, based on \citet{christensen2010}. }
  \label{fig:planetaryB}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Estimate of Radio Intensity of RGHJs in comparison with canonical HJs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Assumptions for Planetary Magnetic Field}
%\label{ss:magneticfield}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
